### 2023-01-24 article.tex
No he/she
Fix typo: 'fictuous' -> 'fictitious'

The conclusions drawn from this paper,
may end up in the clinic.
For the sake of having a clear (yet fictuous) example,
let's assume that a high level of IL6RA 
is associated with a disease that develops later in life,
yet is preventable by lifestyle changes.
Would this be the case, we can create a gene panel that specifically measures
SNP \verb|rs12133641|. 
If the gene panel shows an individual has two guanines, 
we know that this person is likelier to develop higher levels of
IL6RA and is likelier to benefit from the lifestyle changes.

@@

Code has additional useful information, similar to confidence intervals,
that allow a reader to gauge how much he/she trusts the results.
The more of the best practices are followed, 
the more trustworthy are the results.
The most important best practices discussed in this paper are
automatic testing, having a high code coverage and code
of low (cyclomatic) complexity.
In academia, to uncover the truth, code correctness is essential,
similar to cell biologists working sterile to not contaminate their
cell cultures.
These best practices are vital for a computational biologist.

>>>>

The conclusions drawn from this paper,
may end up in the clinic.
For the sake of having a clear (yet fictitious) example,
let's assume that a high level of IL6RA 
is associated with a disease that develops later in life,
yet is preventable by lifestyle changes.
Would this be the case, we can create a gene panel that specifically measures
SNP \verb|rs12133641|. 
If the gene panel shows an individual has two guanines, 
we know that this person is likelier to develop higher levels of
IL6RA and is likelier to benefit from the lifestyle changes.

@@

Code has additional useful information, similar to confidence intervals,
that allow a reader to gauge how much one trusts the results.
The more of the best practices are followed, 
the more trustworthy are the results.
The most important best practices discussed in this paper are
automatic testing, having a high code coverage and code
of low (cyclomatic) complexity.
In academia, to uncover the truth, code correctness is essential,
similar to cell biologists working sterile to not contaminate their
cell cultures.
These best practices are vital for a computational biologist.
